Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction

### 2025-01-18 src/article.tex
test figure

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/side_w-o_sensors.png} 
  \caption{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023} \Description{A 3-Key Model of a Harpsichord Mechanism created Graziano Bandini in Bologna
  2023. A sidevew of the model which is a cross-section of what is a common
mechanism for an italian style harpischord of the XVI century.} 
\end{figure}
